---
title: "reprex"
author: "Allison Horst"
date: "8/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

Your job is to identify an error, then make a reproducible example that would help future you or someone else understand how to write the code correctly. In other words, your reprex code will *work* and offer a solution to the error thrown in each of the following examples. 

Data are in `AS00601.csv` (and read in correctly below as `mack_creek_vertebrates`). 

Data package title: Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present

**Citation:** Gregory, S.V. and I. Arismendi. 2020. Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present ver 14. Environmental Data Initiative. https://doi.org/10.6073/pasta/7c78d662e847cdbe33584add8f809165

### Read in the data 

There are no problems here. 
```{r}
mack_creek_vertebrates <- read_csv(here("AS00601.csv"))
```

### reprex 1

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 1: 
mack_creek_lengths <- mack_creek_vertebrates %>% 
  clean_names() %>% 
  select(year:sampledate) %>% 
  filter(section == "CC") %>% 
  mutate(across(where(is.character, tolower))) %>% 
  drop_na(species) %>% 
  group_by(species) %>% 
  summarize(mean_length_cm = mean(length1, na.rm = TRUE),
            sd_length_cm = sd(length1, na.rm = TRUE)) %>% 
  ungroup()
```

```{r}
#subset
mack_creek_vertebrates_sub <- mack_creek_vertebrates %>% 
  select(SPECIES) %>% 
  slice_head(n = 5)

#datapasta
datapasta::df_paste(mack_creek_vertebrates_sub)

mack_creek_vertebrates_subset <- data.frame(
  stringsAsFactors = FALSE,
           SPECIES = c("ONCL", "ONCL", "ONCL", "ONCL", "ONCL"))

#share
library(tidyverse)

mack_creek_vertebrates_subset <- data.frame(
  stringsAsFactors = FALSE,
           SPECIES = c("ONCL", "ONCL", "ONCL", "ONCL", "ONCL"))

mack_creek_lengths <- mack_creek_vertebrates_subset %>% 
  mutate(across(where(is.character, tolower))) 

#reprex

``` r
library(tidyverse)

mack_creek_vertebrates_subset <- data.frame(
  stringsAsFactors = FALSE,
           SPECIES = c("ONCL", "ONCL", "ONCL", "ONCL", "ONCL"))

mack_creek_lengths <- mack_creek_vertebrates_subset %>% 
  mutate(across(where(is.character, tolower))) 
#> Error in `mutate()`:
#> ℹ In argument: `across(where(is.character, tolower))`.
#> Caused by error in `across()`:
#> ℹ In argument: `where(is.character, tolower)`.
#> Caused by error in `where()`:
#> ! unused argument (tolower)
```
<sup>Created on 2025-08-21 with [reprex v2.1.1](https://reprex.tidyverse.org)</sup>


### reprex 2

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 2:
mack_creek_vertebrates %>% 
  clean_names() %>% 
  filter(species == "ONCL") %>% 
  ggplot(aes(x = length1, y = weight)) +
         geom_point(aes(shape = 12), color = "purple") +
         theme_minimal() +
         labs(x = "Cutthroat trout length (cm)",
              y = "Weight (g)")
```

```{r}
# subset
mack_creek_vertebrates_2 <- mack_creek_vertebrates %>% 
  select(LENGTH1, WEIGHT) %>% 
  slice_head(n = 5)

#datapasta
datapasta::df_paste(mack_creek_vertebrates_2)


mack_creeks_vertebrates_subset2 <- data.frame(
     LENGTH1 = c(58, 61, 89, 58, 93),
      WEIGHT = c(1.75, 1.95, 5.6, 2.15, 6.9)
 )

#share
library(tidyverse)

mack_creeks_vertebrates_subset2 <- data.frame(
     LENGTH1 = c(58, 61, 89, 58, 93),
      WEIGHT = c(1.75, 1.95, 5.6, 2.15, 6.9)
 )

mack_creeks_vertebrates_subset2 %>% 
  ggplot(aes(x = LENGTH1, y = WEIGHT)) +
         geom_point(aes(shape = 12), color = "purple")

#reprex

``` r
library(tidyverse)

mack_creeks_vertebrates_subset2 <- data.frame(
     LENGTH1 = c(58, 61, 89, 58, 93),
      WEIGHT = c(1.75, 1.95, 5.6, 2.15, 6.9)
 )

mack_creeks_vertebrates_subset2 %>% 
  ggplot(aes(x = LENGTH1, y = WEIGHT)) +
         geom_point(aes(shape = 12), color = "purple")
#> Error in `geom_point()`:
#> ! Problem while computing aesthetics.
#> ℹ Error occurred in the 1st layer.
#> Caused by error in `scale_f()`:
#> ! A continuous variable cannot be mapped to the shape aesthetic.
#> ℹ Choose a different aesthetic or use `scale_shape_binned()`.
```

<sup>Created on 2025-08-21 with [reprex v2.1.1](https://reprex.tidyverse.org)</sup>

## End